Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
add a little improvement and alternate interfaces section

%\noindent {\bfseries Improved and Alternative Interfaces} {\color {red} optional section here.}

>>>>

\noindent {\bfseries Improved and Alternative Interfaces} We have yet to design the 
improvements to the interface, as they will be based on the data collected from 
the user studies on the current configuration interface. In general, we will measure the 
time it took to configure correctly, and help users avoid common mistakes. An alternate 
interface to automate the configuration process for the user has been proposed in the 
community. There issue is that the automation make the connection process less transparent, 
and since there are countries who log internet activity, automated attempts to obviously
use the Tor network could have the potential to be incriminating.
